---
title: "linear model from Web"
author: "Kevin Ortega"
date: "October 2024"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

```{r}
plot(SIMS~ARM,data=data)
model.1=lm(SIMS~ARM, data=data)
abline(model.1)
```

This scatter plot shows a positive relationship between simulation score and arm strenght. Simulation strength increases as arm strength increases.

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```
With a correlation of 0.69 There is moderate positive correlation between the SIMS score and ARM strength.


### Inferential  (Build model.1)

```{r}
model.1=lm(SIMS~ARM, data=data)
summary.lm(model.1)
```

The model shows that the intercept and coefficient of ARM are both significantly different from 0.

#### Predict at target point

```{r}
targtPoint = data.frame(GRIP=94, ARM=88)
predictInt = predict(model.1, targtPoint, interval = 'prediction')
print(predictInt)
```

At ARM=88, GRIP=94, the predicted SIMS score is 0.71. At that score the 95% confidence interval for that score is SIMS between -1.73 and 3.14

#### scatterplot with model fit
  

## Model 2 SIM~GRIP

### Now add in scatterplot

```{r}
plot(SIMS~GRIP,data=data)
model.2=lm(SIMS~ARM, data=data)
abline(model.2)
```
This scatter plot shows a positive relationship between simulation score and Grip strength. Simulation strength increases as Grip strength increases.


### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```
With a correlation of 0.64 There is moderate positive correlation between the SIMS score and GRIP strength.

### Inferential  (Build model.2)

```{r}
model.2=lm(SIMS~GRIP, data=data)
summary.lm(model.2)
```
  
The model shows that the intercept and coefficient of GRIP are both significantly different from 0.

#### predict model.2 at target point

```{r}
targtPoint = data.frame(GRIP=94, ARM=88)
predictInt = predict(model.2, targtPoint, interval = 'prediction')
print(predictInt)
```
At ARM=88, GRIP=94, the predicted SIMS score is -0.54. At that score the 95% confidence interval for that score of SIMS is between -3.11 and 2.04

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

```{r}
model.3 = lm(SIMS~ARM+GRIP, data=data)
summary(model.3)
```

Model.3 shows that the intercept -5.434, coefficient 0.038 of ARM, and coefficent of GRIP 0.025 are all sigificantly different from 0. Both have P-Values that are significantly different than 0, so they're helpful in predicting results.

### Numerical results (cor)

```{r}
cor(data)
```
Sims corelate with Arms in these models.  
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
```{r}
predict(model.3, targtPoint,interval='prediction')
```
  


## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

```{r}
# Compare the two models using ANOVA
anova_result <- anova(model.1, model.3)
print(anova_result)
```
The P-Value is less than 0.05 proving that the models are different. Model 2 is better than model 1 because the comparison is better.

```{r}
# Compare the two models using ANOVA
anova_result <- anova(model.2, model.3)
print(anova_result)
```
The P-Value is less than 0.05 proving that the models are different. Model 3 is better than model 2 because the comparison is better.
